---
output:
  md_document;
  github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"cointoss"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to simulate tossing a coin.

*`"bin_distribution()"` creates a data frame showing the distribution of probability  different number of successes in certain number of trials can be displayed.

*`"bin_cumulative()"` creates a data frame showing the distribution of cumulative probability ofdifferent number of successes in certain number of trials can be displayed.

*`"bin_variable()"` exams the summary of the variables and measures.

*there are some function to calculate the measures:

the expected value: `"bin_mean()"`

the variance: `"bin_variance()"`

the mode: `"bin_mode()"`

the skewness: `"bin_skewness()"`

the kurtosis: `"bin_kurtosis"`


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r eval=FALSE}
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("luciachenxl/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("luciachenxl/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)

# probability of getting 2 successes in 5 trials
#(assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

#binomial probability distribution
dis<-bin_distribution(trials = 5, prob = 0.5)
dis

#plot the distribution
plot(dis)

#cumulative binomial probability distribution
dis<-bin_cumulative(trials = 5, prob = 0.5)
dis

#plot the cumulative distribution
plot(dis)

#summary of the variables and measures 
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1

```
