---
title: "Getting started with binomial"
author: "Xiaolu Chen"
date: "04/28/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo= FALSE, message=FALSE}
knitr::opts_chunk$set(collapse= T, comment = "#>")
library(binomial)
```

## Binomial

This package `"binomial"` implements functions for
calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.

## Get the probability of successes trials

With function `"bin_probability()"`, the probability of k successes in n trials can be calculated:

```{r}
# probability of getting 2 successes in 5 trials
#(assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Get the distribution of probabilities of successes

With the function `"bin_distribution()"`, a data frame showing the distribution of probability  different number of successes in certain number of trials can be displayed.

```{r}
#binomial probability distribution
dis<-bin_distribution(trials = 5, prob = 0.5)
dis

#plot the distribution
plot(dis)
```

## Get the cumulative probability

Next, with the function `"bin_cumulative()"`,a data frame showing the distribution of cumulative probability ofdifferent number of successes in certain number of trials can be displayed.

```{r}
#cumulative binomial probability distribution
dis<-bin_cumulative(trials = 5, prob = 0.5)
dis

#plot the cumulative distribution
plot(dis)
```


## Summary

Now, you may want to exam the summary of the variables and measures with function `"bin_variable()"`.

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```

## Measures

Last, there are some function to calculate the measures:

the expected value: `"bin_mean()"`

the variance: `"bin_variance()"`

the mode: `"bin_mode()"`

the skewness: `"bin_skewness()"`

the kurtosis: `"bin_kurtosis"`






